### 2024-10-28 source/cadabra/geodesic-ivp.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

@@

@@

   checkpoint.append (sterm2)
   checkpoint.append (sterm3)
   checkpoint.append (sterm4)
   checkpoint.append (sterm5)
\end{cadabra}

@@

>>>>

\def\Date{30 Jul 2024}
% \def\FileID{file:}

@@

   # note: the various ivp21, ivp31  etc. are the pieces of the Taylor series
   #       for the ivp but *without* the leading 1/n! of the Taylor series

   ivp21 := @(sterm21).                                          # cdb (ivp21.000,ivp21)

   ivp31 := @(sterm21) + @(sterm22).                             # cdb (ivp31.000,ivp31)
   ivp32 := @(sterm31).                                          # cdb (ivp32.000,ivp32)

   ivp41 := @(sterm21) + @(sterm22) + @(sterm23).                # cdb (ivp41.000,ivp41)
   ivp42 := @(sterm31) + @(sterm32).                             # cdb (ivp42.000,ivp42)
   ivp43 := @(sterm41).                                          # cdb (ivp43.000,ivp43)

   ivp51 := @(sterm21) + @(sterm22) + @(sterm23) + @(sterm24).   # cdb (ivp51.000,ivp51)
   ivp52 := @(sterm31) + @(sterm32) + @(sterm33).                # cdb (ivp52.000,ivp52)
   ivp53 := @(sterm41) + @(sterm42).                             # cdb (ivp53.000,ivp53)
   ivp54 := @(sterm51).                                          # cdb (ivp54.000,ivp54)

   factor_out (ivp21,$A^{a?}$)                                   # cdb (ivp21.001,ivp21)

   factor_out (ivp31,$A^{a?}$)                                   # cdb (ivp31.001,ivp31)
   factor_out (ivp32,$A^{a?}$)                                   # cdb (ivp32.001,ivp32)

   factor_out (ivp41,$A^{a?}$)                                   # cdb (ivp41.001,ivp41)
   factor_out (ivp42,$A^{a?}$)                                   # cdb (ivp42.001,ivp42)
   factor_out (ivp43,$A^{a?}$)                                   # cdb (ivp43.001,ivp43)

   factor_out (ivp51,$A^{a?}$)                                   # cdb (ivp51.001,ivp51)
   factor_out (ivp52,$A^{a?}$)                                   # cdb (ivp52.001,ivp52)
   factor_out (ivp53,$A^{a?}$)                                   # cdb (ivp53.001,ivp53)
   factor_out (ivp54,$A^{a?}$)                                   # cdb (ivp54.001,ivp54)

   v{#}::LaTeXForm("\dot{x}").

   substitute (ivp21, $A^{a} -> v^{a}$)                          # cdb (ivp21.002,ivp21)

   substitute (ivp31, $A^{a} -> v^{a}$)                          # cdb (ivp31.002,ivp31)
   substitute (ivp32, $A^{a} -> v^{a}$)                          # cdb (ivp32.002,ivp32)

   substitute (ivp41, $A^{a} -> v^{a}$)                          # cdb (ivp41.002,ivp41)
   substitute (ivp42, $A^{a} -> v^{a}$)                          # cdb (ivp42.002,ivp42)
   substitute (ivp43, $A^{a} -> v^{a}$)                          # cdb (ivp43.002,ivp43)

   substitute (ivp51, $A^{a} -> v^{a}$)                          # cdb (ivp51.002,ivp51)
   substitute (ivp52, $A^{a} -> v^{a}$)                          # cdb (ivp52.002,ivp52)
   substitute (ivp53, $A^{a} -> v^{a}$)                          # cdb (ivp53.002,ivp53)
   substitute (ivp54, $A^{a} -> v^{a}$)                          # cdb (ivp54.002,ivp54)

   # build the Taylor series
   # note the inclusion of the 1/n! factors

   ivp2 := x^{a} + s v^{a} + (1/2) (s**2) @(ivp21).
   ivp3 := x^{a} + s v^{a} + (1/2) (s**2) @(ivp31) + (1/6) (s**3) @(ivp32).
   ivp4 := x^{a} + s v^{a} + (1/2) (s**2) @(ivp41) + (1/6) (s**3) @(ivp42) + (1/24) (s**4) @(ivp43).
   ivp5 := x^{a} + s v^{a} + (1/2) (s**2) @(ivp51) + (1/6) (s**3) @(ivp52) + (1/24) (s**4) @(ivp53) + (1/120) (s**5) @(ivp54).

   # cdb (ivp2.000,ivp2)
   # cdb (ivp3.000,ivp3)
   # cdb (ivp4.000,ivp4)
   # cdb (ivp5.000,ivp5)

   # now construct the scaled terms for ivp5

@@

   checkpoint.append (sterm2)
   checkpoint.append (sterm3)
   checkpoint.append (sterm4)
   checkpoint.append (sterm5)

   cdblib.create ('geodesic-ivp.json')

   cdblib.put ('ivp21',ivp21,'geodesic-ivp.json')

   cdblib.put ('ivp31',ivp31,'geodesic-ivp.json')
   cdblib.put ('ivp32',ivp32,'geodesic-ivp.json')

   cdblib.put ('ivp41',ivp41,'geodesic-ivp.json')
   cdblib.put ('ivp42',ivp42,'geodesic-ivp.json')
   cdblib.put ('ivp43',ivp43,'geodesic-ivp.json')

   cdblib.put ('ivp51',ivp51,'geodesic-ivp.json')
   cdblib.put ('ivp52',ivp52,'geodesic-ivp.json')
   cdblib.put ('ivp53',ivp53,'geodesic-ivp.json')
   cdblib.put ('ivp54',ivp54,'geodesic-ivp.json')

   cdblib.put ('ivp2',ivp2,'geodesic-ivp.json')
   cdblib.put ('ivp3',ivp3,'geodesic-ivp.json')
   cdblib.put ('ivp4',ivp4,'geodesic-ivp.json')
   cdblib.put ('ivp5',ivp5,'geodesic-ivp.json')
\end{cadabra}

@@

\begin{dgroup*}
   \begin{dmath*} \cdb*{ivp21.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp31.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp32.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp41.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp42.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp43.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp51.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp52.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp53.002} \end{dmath*}
   \begin{dmath*} \cdb*{ivp54.002} \end{dmath*}
\end{dgroup*}

\begin{dgroup*}
   \begin{dmath*} \cdb*{ivp2.000} \end{dmath*}
   \begin{dmath*} \cdb*{ivp3.000} \end{dmath*}
   \begin{dmath*} \cdb*{ivp4.000} \end{dmath*}
   % \begin{dmath*} \cdb*{ivp5.000} \end{dmath*}
\end{dgroup*}

### 2024-10-28 source/cadabra/metric-inv.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

>>>>

   # these versions of "metric" are created just to add to the metric.json library
   # note: term1 = 0, I could have used this fact above but ...

   metric2:=@(term0) + @(term2).
   metric3:=@(term0) + @(term2) + @(term3).
   metric4:=@(term0) + @(term2) + @(term3) + @(term4).
   metric5:=@(term0) + @(term2) + @(term3) + @(term4) + @(term5).

   cdblib.put ('g^ab2',metric2,'metric-inv.json')
   cdblib.put ('g^ab3',metric3,'metric-inv.json')
   cdblib.put ('g^ab4',metric4,'metric-inv.json')
   cdblib.put ('g^ab5',metric5,'metric-inv.json')
\end{cadabra}

### 2024-10-28 source/cadabra/metric.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

>>>>

   # these versions of "metric" are created just to add to the metric.json library
   # note: term1 = 0, I could have used this fact above but ...

   metric2:=@(term0) + @(term2).
   metric3:=@(term0) + @(term2) + @(term3).
   metric4:=@(term0) + @(term2) + @(term3) + @(term4).
   metric5:=@(term0) + @(term2) + @(term3) + @(term4) + @(term5).

   cdblib.put ('g_ab2',metric2,'metric.json')
   cdblib.put ('g_ab3',metric3,'metric.json')
   cdblib.put ('g_ab4',metric4,'metric.json')
   cdblib.put ('g_ab5',metric5,'metric.json')
\end{cadabra}
